\startcomponent colophon
\environment    travellayout

\chapter{Colophon}

\section{General}

This is the report of our study tour to Russia which took place in October 2009. The tour was organised by the students' association for physics and astronomy, Marie Curie, of the Radboud University Nijmegen, The Netherlands.
All contributions to this report are by the participants of the tour. The organising committee, however, has made some slight modifications here and there. Still, responsibility for the contents of this report lies completely with the authors of the individual chapters.

Typeset in Lucida \doifmodeelse{reader}{$8/12 \times 25$}{$10/14 \times 34$}, using \CONTEXT.

\section{Organising commitee}

\starttabulate[|l|lI|]
\NC Guus van Aar  \NC Chairman      \NR
\NC Frank Hemmes  \NC Treasurer     \NR
\NC Jins de Jong  \NC Secretary     \NR
\NC Margot Peters \NC Travel report \NR
\stoptabulate

\section{Thanks to}

An enormous event such as a tour through Russia is impossible to organize without the highly appreciated help of others, whose contibutions were of great use to us. Therefore, our gratitude goes out to the following people and
institutes:

\startitemize
\item All hosting institutes in Russia
\item \infull{SMCR} (\SMCR), for helping out and providing us with useful advice
\item \infull{MC}, students' association for physics and astronomy
\item Faculty of Science of the \infull{RU} (\RU)
\item \infull{IMAPP} of the \RU
\item \infull{IMM} of the \RU
\item \infull{HFML} of the \RU
\item \infull{DI} of the \RU
\item \SNUF, \infull{SNUF}
\item \NNV, Dutch Physical Society
\item \FOM, Foundation for Fundamental Research on Matter
\item \EPS, \infull{EPS}
\item Stichting \cap{hef}, Foundation for High-Energy Physics
\item All the people at \emph{RealRussia} for helping us arrange our tour so succesfully.
\item And, last but not least, all of the participants.
\stopitemize

\section{Cover}

A group picture in front of the statue of Michail Lomonosov, in front of the Moscow State University, together with Prof. Granovsky.

\section{Cartoon}

The cartoon that is shown at pages \at[part:stpet], \at[part:mosc], \at[part:tse] and \at[part:novo] is made by Inka Locht, one of the participants of the study tour. 

\section{Address}

\startlines
©~2009–2010 \infull{SMCR}
Faculty of Science
Heyendaalseweg 135
6525 AJ  Nijmegen
The Netherlands
\from[mailto:smcr]
\stoplines

\stopcomponent
